Multi-product Batch Processing Time Maximization Problem

### 2023-08-18 multi-period/manuscript.tex
updating papers
multi-period

@@

@@

$\textrm{Z}$ is the timeout for batch processing; \\

@@

being $\textrm{UI}_{i0}$ the maximum quantity allowed for $P_i$;

@@

being $\textrm{I}_{0}$ the initial free inventory for all products on factory on the start of the (\emph{first}) planning day ($d=1$); \\

@@

\begin{equation}
\label{eq:mmeq03}
P_i + UI_{i1} - D_{i1} - O_{i1} = \textrm{UI}_{i0} - \textrm{PO}_{i1}
\end{equation}

@@

Uma solução ótima para este problema pode ser construída através de duas etapas, conforme explicado a seguir: \\

\emph{etapa 1: distribuição da produção previamente planejada} \\

passo 1: Desconsidere a produção a ser planejada:

\begin{equation}
\label{eq:sm01}
P_i = 0, \forall i
\end{equation}

passo 2:

Calcule $D_{i1}$ usando as equações em (\ref{eq:sm02}):

\begin{equation}
\label{eq:sm02}
D_{i1} = \min \{\textrm{UD}_{i1}, \textrm{PO}_{i1}\} \quad \forall i
\end{equation}

Calcule o valor da produção não ainda não alocada, $\textrm{S}_{id}, \forall i$, pelas equações em (\ref{eq:sm03}):

\begin{equation}
\label{eq:sm03}
\textrm{S}_{i1} = \textrm{PO}_{i1} - D_{i1}, \quad \forall i
\end{equation}

Calcule os valores $D_{id}^+$, $\textrm{S}_{id}^+$, $D_{id}^-$ e $\textrm{S}_{id}^-, \forall i$, usando as equações de (\ref{eq:sm04}) à (\ref{eq:sm08}).

\begin{equation}
\label{eq:sm04}
D_{i1}^+ = D_{i1}^- = D_{i1}
\end{equation}

\begin{equation}
\label{eq:sm05}
D_{id}^+ =  \min\{(\sum_{k=1}^{d}{\textrm{UD}_{ik}} - \sum_{k=1}^{d-1}{D_{ik}}), (\sum_{k=1}^{d-1}{(\textrm{PO}_{ik} - D_{ik}^+) + \textrm{PO}_{id}})\}  \quad \forall i, \forall (d>1)
\end{equation}

\begin{equation}
\label{eq:sm06}
\textrm{S}_{id}^+ = \textrm{PO}_{id} - D_{id}^+, \quad \forall i, \forall (d>1)
\end{equation}

\begin{equation}
\label{eq:sm07}
D_{id}^- =  \min\{(\sum_{k=2}^{d}{\textrm{UD}_{ik}} - \sum_{k=2}^{d-1}{D_{ik}}), (\sum_{k=1}^{d-1}{(\textrm{PO}_{ik} - D_{ik}^-) + \textrm{PO}_{id}})\}  \quad \forall i, \forall (d>1)
\end{equation}

\begin{equation}
\label{eq:sm08}
\textrm{S}_{id}^- = \textrm{PO}_{id} - D_{id}^-, \quad \forall i, \forall (d>1)
\end{equation}

Queremos encontrar $D_{id}$, $ D_{id}^- \leq D_{id} \leq D_{id}^+, \forall i,(d>1) $, tal que as restrições em (\ref{eq:sm09}) sejam respeitadas:

\begin{equation}
\label{eq:sm09}
D_{id} = \min {x \in \{D_{id}^-, D_{id}^+ \quad | \quad UI_{id} \geq 0\}} \quad \forall i, \forall (d>1)
\end{equation}

Contudo, para solução do problema, iremos adotar:

\begin{equation}
\label{eq:sm10}
D_{id} = D_{id}^- \quad \forall i, \forall (d>1)
\end{equation}

\begin{equation}
\label{eq:sm10}
\textrm{S}_{id} = \textrm{S}_{id}^- \quad \forall i, \forall (d>1)
\end{equation}

passo 3: Calcule os valores $O_{id}, \forall i, d$, usando as equações em (\ref{eq:sm11}):

\begin{equation}
\label{eq:sm11}
O_{id} = \min \{\textrm{S}_{id}, (\textrm{UO}_i - \sum_{k=1}^{d-1}{O_{ik}}) , (\textrm{O}- \sum_{j=1}^{i-1}\sum_{k=1}^{d-1}{O_{jk}}) \} \quad \forall i, d
\end{equation}

passo 4:

calcule os valores para $UI_{id}, \forall i, d$, usando as equações em (\ref{eq:mmeq03}) e (\ref{eq:mmeq04})).

calcule os valores para $I_{i}, \forall i$, usando as equações em (5) e (6). \\

\emph{Step 2: MPBPTM problem construction} \\

So, based on calculated values, we built the MPBPTM problem using the equations:

\begin{equation}
\textrm{UD}_{i} = \textrm{UD}_{i1} - D_{i1} \quad \forall i
\end{equation}

\begin{equation}
\textrm{I} = \min_{d} \{I_{d}\}
\end{equation}

\begin{equation}
\textrm{UI}_{i} = \min_{d} \{UI_{id}\}, \quad \forall{i}
\end{equation}

\begin{equation}
\textrm{O} = \textrm{O} - \sum_{i}{\sum_{d}{O_{id}}}
\end{equation}

\begin{equation}
\textrm{UO}_{i} = \textrm{UO}_{i} - \sum_{d}{O_{id}}, \quad \forall i
\end{equation} \\

Being $\textrm{p}_{i}$ and $\textrm{Z}$ defined according to the MPMPBPTM problem presented. \\

Obs: Note that some values of $UI_{id}$ and  $I_{d}$ can be negative. This means that, in prior planning, some demand of the first day will be met by some previous planned production performed in a future period and that cannot be modified, i.e. $D_{id} > D_{id}^-$ for at least one ordained pair $(i,d)$. In this case, considering that prior planning was a viable planning, the negative values of the $UI_{id}$ and $I_{d}$ will be offset by the positive surplus values of $\textrm{UD}_{i}$, so this will not result in change in the optimal solution of the problem through the method used in the next step. \\

The possible negative maximum values for variables are defined by the following equations. If this equations are not met, it means that initial planning was not a viable planning.

\begin{equation}
\max_d\{UI_{id}\} \geq \textrm{UD}_{i1} - D_{i1}, \quad \forall i
\end{equation}

\begin{equation}
\max_d\{I_{d}\} \geq \sum_{i}\{ \textrm{UD}_{i1} - D_{i1} \}
\end{equation}

\emph{Step 3: MPBPTM solution by Fraga's analytical method} \\

Once the MPBPTM problem is built, it can be solved by the analytical method proposed by Fraga (Fraga et al., 2023). This method can be resumed into two steps, as follows: \\

step 1: find $T^*$, where:
\begin{equation}
T^* = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
\end{equation}

step 2: calculate $T$, where:

\begin{equation}
T = \min \{T^* , \textrm{Z}\}
\end{equation} \\

\emph{Solution for the example presented before} \\

Applying the method for solving the example presented in section \ref{sec:MBPTMP}, we have: \\

Como planejamento prévio de produção, temos:

$\textrm{P}_{11} = 1000$,
$\textrm{P}_{12} = 0$,
$\textrm{P}_{21} = 0$,
$\textrm{P}_{22} = 1500$. \\

Como demanda, temos:

$\textrm{UD}_{11} = 1000$,
$\textrm{UD}_{12} = 500$,
$\textrm{UD}_{21} = 500$,
$\textrm{UD}_{22} = 300$. \\

Distribuindo a produção para atender à demanda de acordo com as restrições em (9) e (10), temos: \\

$D_{11} = 1000$,
$D_{12} = 0$,
$D_{21} = 0$,
$D_{22} = 300$. \\

Não há nenhuma sobra relativa a produção de A. E há uma sobra de produção de 1200 unidades de B no segundo dia. \\

Como estoque livre nos outlets, temos:

$\textrm{UO}_{1} = 600$;
$\textrm{UO}_{2} = 600$;
$\textrm{O} = 1000$; \\

Assim, distribuindo a sobra da produção para os outlets de acordo com as restrições em (7) e (8), temos:

$O_{11} = 0$,
$O_{12} = 0$,
$O_{21} = 0$,
$O_{22} = 600$. \\

Com relação ao estoque livre em fábrica, temos:

$\textrm{UI}_{10} = 3000$,
$\textrm{UI}_{20} = 2000$,
$\textrm{I}_{0} = 3000$. \\

Portanto, calculando os valores disponíveis para produção de acordo com as equações em (3), (4) e (5), temos:

$UI_{11} = 3000 - 1000 + 1000 + 0 =  3000$,
$UI_{12} = 3000 - 0 + 0 + 0 =  3000$,
$UI_{21} = 2000 - 0 + 0 + 0 =  2000$,
$UI_{22} = 2000 - 1500 + 300 + 600 =  1400$. \\

$I_{1} = 3000 - 1000 + 1000 + 0 = 3000$,
$I_{2} = 3000 - 1500 + 300 + 600 = 2400$. \\

Portanto temos agora as informações referentes aos limites estocagem em fábrica diário para cada produto assim como o limite de estocagem em fábrica diário para todos os produtos. \\

Definindo o problema MPBPTM, temos: \\

$\textrm{UD}_{1} = 1000 - 1000 = 0$,
$\textrm{UD}_{2} = 0$ . \\

$\textrm{I} = \min_{d} \{3000, 2400\} = 2400$. \\

$ \textrm{UI}_{1} = \min_{d} \{3000, 3000\} = 3000 $,
$ \textrm{UI}_{2} = \min_{d} \{2000, 1400\} = 1400 $. \\

$\textrm{O} = 1000 - 600 = 400.$ \\

$\textrm{UO}_{1} = 600 - 0 = 600$, 
$\textrm{UO}_{2} = 600 - 600 = 0$. \\

$\textrm{p}_{1} = 60$,
$\textrm{p}_{2} = 40$.  \\

$\textrm{Z} = 100$.  \\

Então, aplicando o método de partição do tempo proposto pro Fraga, temos: \\

$T' = 0 \textrm{ min}$ \\

Then:\\

$S_A = 0 \textrm{ g}$ \\

$S_B = 0 \textrm{ g}$ \\

And so we have: \\

$T'' \leq \lfloor{(3000 \textrm{ g} + 600 \textrm{ g} + 0 \textrm{ g}) / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\

$T'' \leq 60 \textrm{ min}$ \quad for A \\

$T'' \leq \lfloor{(1400 \textrm{ g} + 0 \textrm{ g} + 0 \textrm{ g}) / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\

$T'' \leq 35 \textrm{ min}$ \quad for B \\

$T'' \leq \lfloor{(400 \textrm{ g} + 2400 \textrm{ g} + 0 \textrm{ g}) / (100 \textrm{ g}/\textrm{min})}\rfloor$ \\

$T'' \leq 28 \textrm{ min}$ \quad for A and B \\

So that: \\

$T'' = 28 \textrm{ min}$ \\

So we have: \\

$T = 28 \textrm{ min}$ \\

As $T<\textrm{Z}$, then $T = 28 \textrm{ min}$ will certainly be the optimal solution. \\

In this case we will have: \\

$P_A = 1,680  \textrm{ g}$ e $P_B=1,120 \textrm{ g}$ \\

$D_A = 0 \textrm{ g}$ e $D_B = 0 \textrm{ g}$ \\

$E_A = 1,680 \textrm{ g}$ e $E_B = 1,120 \textrm{ g}$ \\

>>>>

\usepackage{algorithm}
\usepackage{algpseudocode}

@@

$\textrm{UI}_i$ is the factory free inventory for product $p$ on day 0;

@@

$\textrm{Z}$ is the timeout for batch processing;

@@

@@

being $\textrm{I}$ the initial free inventory for all products on factory on the start of the (\emph{first}) planning day ($d=1$); \\

@@

\begin{equation}
\label{eq:mmeq03}
P_i + UI_{i1} - D_{i1} - O_{i1} = \textrm{UI}_{i} - \textrm{PO}_{i1}
\end{equation}

@@

Uma solução ótima para este problema pode ser construída através de seis etapas, conforme algoritmos apresentados a seguir: \\

\begin{algorithm}
\caption{Solving MMBPTM problem | Part 01 - distribution planned production ignoring restrictions defined for the set.}\label{alg:part01}
\begin{algorithmic}
	\Require $\textrm{UD}_{id}, \textrm{PO}_{id}, \textrm{UO}_i, \textrm{UI}_i, \forall i; \textrm{O}, \textrm{I}$.

	\State $I_{1} \gets \textrm{I} - \sum\{\textrm{PO}_{i1}\}$
	\State $O \gets \textrm{O}$

	\For{all $i$}
		\State $D_{i1} \gets \min \{\textrm{UD}_{i1}, \textrm{PO}_{i1}\}$
		\State $UI_{i1} \gets \textrm{UI}_i - \textrm{PO}_{i1} + D_{i1}$
		\State $I_{1} \gets I_{1} + D_{i1}$

		\If{$UI_{i1} < 0$}
			\State $O_{i1} \gets - UI_{i1}$
			\State $UO_i \gets \textrm{UO}_i - O_{i1}$
			\State $O \gets O - O_{i1}$
			\State $I_{1} \gets I_{1} + O_{i1}$
			\State $UI_{i1} \gets 0$
			\If{$UO_i < 0 \textbf{ or } O < 0$}
			\State \textbf{Return:} planning is not feasible
			\EndIf
		\EndIf
	\EndFor

	\For{all $d>1$}

		\State $I_{d} \gets  I_{d-1} - \sum\{\textrm{PO}_{id}\}$

		\For{all $i$}
			\State $UD_{id} \gets \sum_{k=1}^{d}\{\textrm{UD}_{ik}\} - \sum_{k=1}^{d-1}\{D_{ik}\}$
			\State $A_{id} \gets \min\{\sum_{k=1}^{d-1}\{\textrm{PO}_{ik} - D_{ik} - O_{ik}\}\}  + 						\textrm{PO}_{id}$ 
			\State $D_{id} \gets  \min\{UD_{id}, A_{id}\}$
			\State $UI_{id} \gets UI_{i(d-1)} - \textrm{PO}_{id} + D_{id}$

			\State $I_{d} \gets I_{d} + D_{id}$

			\If{$UI_{id} < 0$}
				\State $O_{i1} = - UI_{i1}$
				\State $UO_i = UO_i - O_{id}$
				\State $O \gets O - O_{id}$
				\State $I_{d} \gets I_{d} + O_{id}$
				\State $UI_{id} = 0$
				\If{$UO_i < 0 \textbf{ or } O < 0$}
					\State \textbf{Return:} planning is not feasible
				\EndIf
			\EndIf
		\EndFor
	\EndFor

	\State \textbf{Return:} $O_{id}, UI_{id}, \forall (i, d); I_d, \forall d; UO_i, \forall i; O$.
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Solving MMBPTM problem | Part 02 - adjustment for atteining feasiability.}\label{alg:part02}
\begin{algorithmic}
	\Require $O_{id}, UI_{id}, \forall (i, d); I_d, \forall d; UO_i, \forall i; O$.

	\For{all $d$}
		\If{$I_{d} < 0$}
			\For{all $i$}
				\If{$UO_i \geq |I_{d}|$}
					\State $O_{id} \gets O_{id} - I_{d}$
					\State $UO_i \gets UO_i + I_{d}$
					\State $O \gets O + I_{d}$
					\For{all $k \geq d$}
						\State $UI_{ik} \gets UI_{ik} - I_{d}$
						\State $I_{k} \gets I_{k} - I_{d}$
					\EndFor
					\State break;
				\Else 
					\State $O_{id} \gets O_{id} + UO_i$
					\State $UO_i \gets 0$
					\State $O \gets O - UO_i$
					\For{all $k \geq d$}
						\State $UI_{ik} \gets UI_{ik} + UO_i$
						\State $I_{k} \gets I_{k} + UO_i$
					\EndFor
				\EndIf
			\EndFor
		\EndIf
	\EndFor

	\State \textbf{Return:} $O_{id}, UI_{id}, \forall (i, d); I_d, \forall d; UO_i, \forall i; O$.
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Solving MMBPTM problem | Part 03 - generating a MBPTM problem.}\label{alg:part03}
\begin{algorithmic}
	\Require $O_{id}, UI_{id}, \forall (i, d); I_d, \forall d; UO_i, \forall i; O$.

	\For{all $i$}
		\State $\textrm{UD}_{i} = UD_{i1}$
		\State $\textrm{UO}_i = UO_i$
		\State $\textrm{UI}_i = \min_d\{UI_{id}\}$
	\EndFor

	\State $\textrm{O} = O$
	\State $\textrm{I} = \min_d\{I_{d}\}$

	\State \textbf{Return:} $\textrm{UD}_{i}, \textrm{UO}_i, \textrm{UI}_i, \forall i; \textrm{O}, \textrm{I}$.
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Solving MMBPTM problem | Part 04 - find an optimal $T$ to the MBPTM problem.}\label{alg:part04}
\begin{algorithmic}
	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}$
	\State $T^* \gets \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor$
	\State $T \gets \min \{T^* , \textrm{Z}\}$
\State \textbf{Return:} $T$.
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Solving MMBPTM problem | Part 05 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions defined for the set.}\label{alg:part05}
\begin{algorithmic}
	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}, T$.
	\For{all i}
		\State $P_i \gets T * \textrm{p}_i$
		\State $D_i \gets \min \{\textrm{UD}_i, E_i\}$
		\State $E_i \gets P_i - D_i$
		\State $O_i \gets \min \{\textrm{UO}_i, E_i\}$
		\State $E_i = E_i - O_i$
		\State $\textrm{UO}_i = \textrm{UO}_i - O_i$
		\State $I_i = E_i$
		\State $\textrm{UI}_i = \textrm{UI}_i - I_i$
	\EndFor
	\State $SO = \textrm{O} - \sum_i{O_i}$
	\State $SI = \textrm{I} - \sum_i{I_i}$
	\State \textbf{Return:} $D_i, O_i, I_i, P_i, E_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Solving MMBPTM problem | Part 06: redistribute production to comply with limitation restrictions for the batch products set.}\label{alg:part06}
\begin{algorithmic}
\Require $O_i, I_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
\If{$SO < 0$}
\For{all $i$}
	\State $O_i \gets O_i - \min\{ O_i, UI_i, |SO|\}$
	\State $I_i \gets I_i + \min\{ O_i, UI_i, |SO|\}$
	\State $SO \gets SO + \min\{ O_i, UI_i, |SO|\}$
	\If{$SO = 0$}
		break looping for;
	\EndIf
\EndFor
\EndIf

\If{$SI < 0$}
\For{all $i$}
	\State $I_i \gets I_i - \min\{ I_i, UO_i, |SI|\}$
	\State $O_i \gets O_i + \min\{ I_i, UO_i, |SI|\}$
	\State $SI \gets SI + \min\{ I_i, UO_i, |SI|\}$
	\If{$SI = 0$}
		break looping for;
	\EndIf
\EndFor
\EndIf
\State \textbf{Return:} $O_i, I_i, \forall i$.
\end{algorithmic}
\end{algorithm}

### 2023-08-18 titlePage.tex
updating papers
multi-period

\begin{abstract}
In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates. The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch. In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MBPTM) problem. We also present a mathematical model for the MPBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
\end{abstract}
%%Graphical abstract
%\begin{graphicalabstract}
%\end{graphicalabstract}

>>>>

\begin{abstract}
In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates. The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch. In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MBPTM) problem. We also present a mathematical model for the MBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
\end{abstract}
%%Graphical abstract
%\begin{graphicalabstract}
%\end{graphicalabstract}
